\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-25 paper.tex
conclusion updated

\textbf{Traffic engineering for WAN.}
Optimizing WAN performance is a big challenge.
Prior technologies such as OSPF\cite{OSPF} and MPLS tunnels \cite{MATE,Tightrope} can improve the backbone traffic transfer under the knowledge of traffic demands.
Recently, SDN is widely used in WAN TE.
SWAN\cite{swan}, B4\cite{B4,hong2018b4}, Bwe\cite{bwe},OWAN\cite{OWAN} leverage the whole network information to allocate network bandwidth.
Network scheduling schemes \cite{calendaring,dynamic,D3} also use SDN technology to decide the priority of traffic.
Although these schemes can improve the network utilization, they ignore the \textit{risk} of networks, thus, service availability can't be guaranteed.
%\cite{,evole,Teavar,,FFC,,dynamic,SMORE,,OWAN}.

\textbf{Network risk based traffic engineering.}
\cite{evole} studies the network failures and proposes the principles to design robust network, but it doesn't contain any TE framework.
\cite{Optical} suggests that backbone traffic engineering strategies should consider current and past optical layer performance.
Neither \cite{evole} nor \cite{Optical} contains TE frameworks.
 \cite{Stochastic} models demand and risks as uncertainty, but it can't provide availability at the particular level (e.g., 90\%).
 \cite{bi2019uncertainty-aware} can adjust traffic according to demands, but it ignores the link failures.
 Most of the traffic engineering schemes work in the \textit{reactive} manner, such as \cite{jointfailure},\cite{R3}.
The reactive methods could take a long time to recover from faults, while applications have already been hurt\cite{FFC}.
FFC \cite{FFC} and TEAVAR\cite{Teavar} are proactive routing protection methods, but they can't ensure the resources of services under network failures.
%In this case, FFC \cite{FFC} advocates to take link failure into consideration when allocating network resources.
%Traffic are freedom from congestion under arbitrary combinations of up to $k$ faults with FFC.
%However, FFC will lead to low link utilization.
%To relieve this, TEAVAR\cite{Teavar} considers the probability of link failure and tries to maximize link utilization under the particular availability target.
%Although TEAVAR tries to fully utilize the link capacity, it ignores the availability difference of applications.
%Moreover, both FFC and TEAVAR uses connectivity-based availability, which can't ensure the resources of applications under network failures.
$\mathsf{BATE}$ makes a further step and tries to provide service level bandwidth-based availability.
The availability of $\mathsf{BATE}$ is stronger than them.

\textbf{Bandwidth guarantee.}
Up still now, many existing works have already considered to guarantee the bandwidth of applications over inter or intra DCs.
Deadline-aware schemes such as D$^2$TCP\cite{D2TCP}, LPD \cite{LPD}, Amoeba\cite{Guaranteeings}  try to make flows finish before a fixed time constraints,
but they can't perform finely grained rate limits.
Some cloud bandwidth limit technologies such as CloudMirror \cite{appdriven} and EyeQ \cite{EyeQ}, can provide bandwidth guarantees to applications or tenants, while they ignore the network risks and service availability requirements.
$\mathsf{BATE}$ is different from in two aspects.
Firstly, $\mathsf{BATE}$ considers the network failures and tries to perform rate limit under the assumption.
Secondly, $\mathsf{BATE}$ can guarantee bandwidth at a particular level (e.g., 99\%).

%\begin{figure}[t]
%\begin{center}
%\includegraphics [width=0.9\columnwidth] {fig/evaluation/error.pdf}
%\caption{Total profits comparison.}
%\label{sim-error}
%\end{center}
%\end{figure}
\section{Conclusion Remarks}
We present $\mathsf{BATE}$, a framework that attempts to guarantee the availability demands of applications.
 $\mathsf{BATE}$ aims to optimize the total profits of service subject availability targets.
We design greedy and network scenario pruning algorithm to derive the solution.
We evaluate the performance of $\mathsf{BATE}$ in real testbed as well as trace-driven simulations.
The evaluation results demonstrate that $\mathsf{BATE}$ can improve  bandwidth-based availability performance by up to 50\%.

>>>>

Optimizing WAN performance is a big challenge. One important topic is on network utilization or fairness. 
For example, early studies focus more on tuning parameters of widely used routing protocols, such as OSPF \cite{OSPF} and MPLS \cite{MATE,Tightrope}, for given traffic matrices. 
Recently, Software defined network (SDN) based technologies, including SWAN\cite{swan}, B4\cite{B4,hong2018b4}, Bwe\cite{bwe} and OWAN\cite{OWAN}, rely on a centralized view to optimize 
bandwidth allocations. 
There are also scheduling algorithms \cite{calendaring,dynamic,D3} using SDN to prioritize WAN traffic.
These work mainly consider aggregated traffic in a macro level, while $\mathsf{BATE}$ handles traffic demands of users. 
%Although these schemes can improve the network utilization, they ignore the \textit{risk} of networks, thus, service availability can't be guaranteed.
%\cite{,evole,Teavar,,FFC,,dynamic,SMORE,,OWAN}.

As more applications are depolyed in cloud or datacenters, 
many work study how to provide performance guarantee for intra-DC or inter-DC user traffic, 
including flow deadline \cite{D2TCP, LPD, Guaranteeings} and flow rate \cite{appdriven, EyeQ}.
However, they do not provide adquate mechanisms to deal with potential or actual failures.

Network failures (or uncertainties) have also been considered in various aspects for large scale network evnironments, including design datacenter networks \cite{evole} and optical networks \cite{Optical},  
stochastic models \cite{Stochastic} \cite{bi2019uncertainty-aware}
and failure recovery methods \cite{jointfailure, R3}. 
$\mathsf{BATE}$ studies both proactive and reactive traffic engineering schemes to 
take network failures into account, so that violations on service level agreements can be avoided or mitigated. 
As far as we know, FFC \cite{FFC} and TEAVAR \cite{Teavar} are two pieces of work that are 
most close to $\mathsf{BATE}$, 
in the sense that they also try to provide certain performance guarantee for inter-DC WAN, even under failures. 
However, they have not taken into account the heterogeneities and competitions of user demands, 
and the economic interests of service providers.

\iffalse
\cite{evole} studies the network failures and proposes the principles to design robust network, but it doesn't contain any TE framework.
\cite{Optical} suggests that backbone traffic engineering strategies should consider current and past optical layer performance.
Neither \cite{evole} nor \cite{Optical} contains TE frameworks.
 \cite{Stochastic} models demand and risks as uncertainty, but it can't provide availability at the particular level (e.g., 90\%).
 \cite{bi2019uncertainty-aware} can adjust traffic according to demands, but it ignores the link failures.
 Most of the traffic engineering schemes work in the \textit{reactive} manner, such as \cite{jointfailure},\cite{R3}.
The reactive methods could take a long time to recover from faults, while applications have already been hurt\cite{FFC}.
FFC \cite{FFC} and TEAVAR\cite{Teavar} are proactive routing protection methods, but they can't ensure the resources of services under network failures.

%In this case, FFC \cite{FFC} advocates to take link failure into consideration when allocating network resources.
%Traffic are freedom from congestion under arbitrary combinations of up to $k$ faults with FFC.
%However, FFC will lead to low link utilization.
%To relieve this, TEAVAR\cite{Teavar} considers the probability of link failure and tries to maximize link utilization under the particular availability target.
%Although TEAVAR tries to fully utilize the link capacity, it ignores the availability difference of applications.
%Moreover, both FFC and TEAVAR uses connectivity-based availability, which can't ensure the resources of applications under network failures.

\textbf{Bandwidth guarantee.}
Up still now, many existing works have already considered to guarantee the bandwidth of applications over inter or intra DCs.
Deadline-aware schemes such as D$^2$TCP\cite{D2TCP}, LPD \cite{LPD}, Amoeba\cite{Guaranteeings}  try to make flows finish before a fixed time constraints,
but they can't perform finely grained rate limits.
Some cloud bandwidth limit technologies such as CloudMirror \cite{appdriven} and EyeQ \cite{EyeQ}, can provide bandwidth guarantees to applications or tenants, while they ignore the network risks and service availability requirements.
$\mathsf{BATE}$ is different from in two aspects.
Firstly, $\mathsf{BATE}$ considers the network failures and tries to perform rate limit under the assumption.
Secondly, $\mathsf{BATE}$ can guarantee bandwidth at a particular level (e.g., 99\%). 
\fi
%\begin{figure}[t]
%\begin{center}
%\includegraphics [width=0.9\columnwidth] {fig/evaluation/error.pdf}
%\caption{Total profits comparison.}
%\label{sim-error}
%\end{center}
%\end{figure}
\section{Conclusion}
We present $\mathsf{BATE}$, a framework that attempts to satisify the heterogeneous bandwidth demands of different users or applications under network failures. 
$\mathsf{BATE}$ is composed of three core components, i.e., admission control, traffic scheduling and failure recovery. They explicitly take failure probabilities into account, while the last 
component also deals with real failures, all in an efficient way. 
Our extensive evaluations show that, it can achieve close to optimal performance guarantee 
and economic profit.

\iffalse
$\mathsf{BATE}$ aims to optimize the total profits of service subject availability targets.
We design greedy and network scenario pruning algorithm to derive the solution.
We evaluate the performance of $\mathsf{BATE}$ in real testbed as well as trace-driven simulations.
The evaluation results demonstrate that $\mathsf{BATE}$ can improve  bandwidth-based availability performance by up to 50\%.
\fi
